Identifying `rtrees` Training Data

### 2020-09-28 journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.Rmd
added next section to work on

# Old Code

<!-- ```{r} -->
<!-- rtrees <- bulletxtrctr::rtrees -->
<!-- paper_rf <- readRDS("../../../diagnostics-paper/data/bullet-rf.rds") -->
<!-- ``` -->

<!-- Extract the features used to fit `rtrees`: -->

<!-- ```{r} -->
<!-- bullet_features <- rownames(bulletxtrctr::rtrees$importance) -->
<!-- bullet_features -->
<!-- ``` -->

<!-- # `rtrees` versus paper model -->

<!-- The code below was used to fit the random forest in the paper but is not run here: -->

<!-- ```{r eval = FALSE} -->
<!-- set.seed(20160104) -->
<!-- bullet_rf <- -->
<!--   randomForest( -->
<!--     y = factor(bullet_train$samesource), -->
<!--     x = bullet_train %>% select(all_of(bullet_features)), -->
<!--     ntree = bulletxtrctr::rtrees$ntree, -->
<!--     mtry = bulletxtrctr::rtrees$mtry -->
<!--   ) -->
<!-- ``` -->

<!-- Confusion matrices from the two models: -->

<!-- ```{r} -->
<!-- rtrees$confusion -->
<!-- paper_rf$confusion -->
<!-- ``` -->

<!-- Variable importance values: -->

<!-- ```{r} -->
<!-- vi = data.frame( -->
<!--   features = rownames(rtrees$importance), -->
<!--   rtrees = rtrees$importance[, 1], -->
<!--   paper = paper_rf$importance[, 1] -->
<!-- ) -->
<!-- ``` -->

<!-- # New Random Forests -->

<!-- Randomly select 100 seeds (using a random seed):  -->

<!-- ```{r} -->
<!-- set.seed(20200917) -->
<!-- seeds = sample(x = 10000000:100000000, size = 100, replace = FALSE) -->
<!-- seeds -->
<!-- ``` -->

<!-- Function for fitting random forests to mimic rtrees with different seeds: -->

<!-- ```{r} -->
<!-- fit_rf <- function(seed) { -->
<!--   set.seed(seed) -->
<!--   bullet_rf <- -->
<!--     randomForest( -->
<!--       y = factor(bullet_train$samesource), -->
<!--       x = bullet_train %>% select(all_of(bullet_features)), -->
<!--       ntree = bulletxtrctr::rtrees$ntree, -->
<!--       mtry = bulletxtrctr::rtrees$mtry -->
<!--     )   -->
<!-- } -->
<!-- ``` -->

<!-- Fit 100 new random forests and save or load: -->

<!-- ```{r} -->
<!-- # Fit (and save) or load random forests -->
<!-- bullet_rfs_file = "../../../data/bullet_rfs.rds" -->
<!-- if (!file.exists(bullet_rfs_file)) { -->
<!--   bullet_rfs = map(.x = seeds, .f = fit_rf) -->
<!--   saveRDS(object = bullet_rfs, file = bullet_rfs_file) -->
<!-- } else { -->
<!--   bullet_rfs = readRDS(bullet_rfs_file) -->
<!-- } -->
<!-- ``` -->

<!-- Function for extracting the confusion matrices from the model and put in a nice data frame: -->

<!-- ```{r} -->
<!-- extract_confus <- function(model) { -->
<!--   data.frame(model$confusion) %>% -->
<!--   rename("FALSE" = "FALSE.", "TRUE" = "TRUE.", "class_error" = "class.error") %>% -->
<!--   mutate(observed = rownames(model$confusion)) %>% -->
<!--   pivot_wider(names_from = observed, values_from = everything())   -->
<!-- } -->
<!-- ``` -->

<!-- Function for extracting the importance values, computing the rank of the features based on importance, and putting in a data frame:  -->

<!-- ```{r} -->
<!-- extract_importance <- function(model) { -->
<!--   data.frame(model$importance) %>% -->
<!--     mutate(features = rownames(model$importance)) %>% -->
<!--     arrange(desc(MeanDecreaseGini)) %>% -->
<!--     mutate(rank = 1:n()) %>% -->
<!--     rename("importance" = "MeanDecreaseGini") %>% -->
<!--     select(features, importance, rank) -->
<!-- } -->
<!-- ``` -->

<!-- Extract the confusion matrices and importance values from all random forest models: -->

<!-- ```{r} -->
<!-- res_confus <- map_df(.x = bullet_rfs, .f = extract_confus, .id = "rf_model_id") -->
<!-- res_importance <- map_df(.x = bullet_rfs, .f = extract_importance, .id = "rf_model_id") -->
<!-- ``` -->

<!-- # Visualizations of Results -->

<!-- ## Class Errors -->

<!-- Obtain the class errors from `rtrees` and the paper random forest: -->

<!-- ```{r} -->
<!-- comparison_values <- -->
<!--   data.frame( -->
<!--     model = c("paper", "rtrees"), -->
<!--     class_error_true = c(paper_rf$confusion[2, 3], rtrees$confusion[2, 3]), -->
<!--     class_error_false = c(paper_rf$confusion[1, 3], rtrees$confusion[1, 3]) -->
<!--   ) -->
<!-- ``` -->

<!-- Histograms of the class errors (true and false) show that the rtrees values appear to be in the extreme (false) or outside of the new random forest models (true): -->

<!-- ```{r fig.width = 10, fig.height = 4.5} -->
<!-- hist_true <-  -->
<!--   res_confus %>% -->
<!--   ggplot(aes(x = class_error_TRUE)) + -->
<!--   geom_histogram() + -->
<!--   geom_vline(data = comparison_values, -->
<!--              mapping = aes(xintercept = class_error_true, color = model)) -->

<!-- hist_false <-  -->
<!--   res_confus %>% -->
<!--   ggplot(aes(x = class_error_FALSE)) + -->
<!--   geom_histogram() + -->
<!--   geom_vline(data = comparison_values, -->
<!--              mapping = aes(xintercept = class_error_false, color = model)) -->

<!-- plot_grid(hist_true, hist_false) -->
<!-- ``` -->

<!-- Class error for TRUE versus class error for FALSE and again the rtrees observations falls outside the range of the newly trained random forest models: -->

<!-- ```{r} -->
<!-- ggplot() + -->
<!--   geom_point(data = res_confus, -->
<!--              mapping = aes(x = class_error_FALSE, y = class_error_TRUE)) + -->
<!--   geom_point( -->
<!--     data = comparison_values, -->
<!--     mapping = aes(x = class_error_false, y = class_error_true, color = model) -->
<!--   ) -->
<!-- ``` -->

<!-- ## Variable Importance  -->

<!-- Prepare variable importance from `rtrees` and paper models for plotting: -->

<!-- ```{r} -->
<!-- vi_ranks <-  -->
<!--   vi %>% -->
<!--   arrange(desc(rtrees)) %>% -->
<!--   mutate(rtrees_rank = 1:n()) %>%  -->
<!--   arrange(desc(paper)) %>% -->
<!--   mutate(paper_rank = 1:n()) %>% -->
<!--   select(-rtrees, -paper) %>% -->
<!--   pivot_longer(names_to = "rf_model_id", values_to = "rank", cols = -features) -->
<!-- ``` -->

<!-- Tile plot showing the variable importance ranks for each model showing variability across newly trained models and some agreement (ex: rough_cor and ccf) and some disagreement (ex: sum_peaks and non_cms) with `rtrees`: -->

<!-- ```{r fig.width = 10, fig.height = 4.5} -->
<!-- rtrees_var_order <- -->
<!--   vi_ranks %>% -->
<!--   filter(rf_model_id == "rtrees_rank") %>% -->
<!--   arrange(desc(rank)) %>% -->
<!--   pull(features) -->

<!-- tile_org <- -->
<!--   vi_ranks %>% -->
<!--   mutate( -->
<!--     rank = factor(rank, levels = 1:9), -->
<!--     features = factor(features, levels = rtrees_var_order),  -->
<!--     rf_model_id = factor(rf_model_id, levels = c("rtrees_rank", "paper_rank")) -->
<!--   ) %>% -->
<!--   ggplot(aes(x = rf_model_id, y = features, fill = rank)) + -->
<!--   geom_tile() + -->
<!--   scale_fill_brewer(palette = "RdYlBu") -->

<!-- tile_new <- -->
<!--   res_importance %>% -->
<!--   mutate( -->
<!--     rank = factor(rank, levels = 1:9), -->
<!--     features = factor(features, levels = rtrees_var_order) -->
<!--   ) %>% -->
<!--   ggplot(aes(x = rf_model_id, y = features, fill = rank)) + -->
<!--   geom_tile() + -->
<!--   scale_fill_brewer(palette = "RdYlBu") -->

<!-- plot_grid(tile_org, tile_new) -->
<!-- ``` -->

<!-- Box plot of ranks across the models with colored points added for the `rtrees` and paper model variable importance ranks (features ordered by `rtrees` variable importance): -->

<!-- ```{r} -->
<!-- res_importance %>% -->
<!--   mutate(features = factor(features, levels = rtrees_var_order)) %>% -->
<!--   ggplot() + -->
<!--   geom_boxplot(aes(x = rank, y = features)) + -->
<!--   geom_jitter( -->
<!--     data = vi_ranks, -->
<!--     mapping = aes(x = rank, y = features, color = rf_model_id), -->
<!--     width = 0, -->
<!--     height = 0.2 -->
<!--   ) -->
<!-- ``` -->

<!-- Features versus variable importance ranks for new models (black lines and points) and `rtrees` and paper model (features ordered by `rtrees` variable importance): -->

<!-- ```{r} -->
<!-- res_importance %>% -->
<!--   mutate( -->
<!--     rank = factor(rank, levels = 1:9), -->
<!--     features = factor(features, levels = rtrees_var_order) -->
<!--   ) %>% -->
<!--   ggplot(aes(x = rank, y = features, group = rf_model_id)) + -->
<!--   geom_line(alpha = 0.2, size = 2) + -->
<!--   geom_point(alpha = 0.2, size = 3) + -->
<!--   geom_line( -->
<!--     data = vi_ranks, -->
<!--     mapping = aes( -->
<!--       x = rank, -->
<!--       y = features, -->
<!--       group = rf_model_id, -->
<!--       color = rf_model_id -->
<!--     ) -->
<!--   ) + -->
<!--   geom_jitter( -->
<!--     data = vi_ranks, -->
<!--     mapping = aes(x = rank, y = features, color = rf_model_id), -->
<!--     width = 0.1, -->
<!--     height = 0 -->
<!--   ) + -->
<!--   labs(title = "new random forest lines and points created with alpha shading") -->
<!-- ``` -->

>>>>

# Training New Random Forests
